Uncertainty propagation in deep neural networks for sparse coding

### 2018-03-09 paper/BayesianLISTA.tex
return old lemma overview to keep it complete for now

%lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft-thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$. Overall the probabilistic layer is described by theorem \ref{thm:prob_layer}.

>>>>

Lemma \ref{thm:matrix_const} describes the probabilistic variant of \textsc{lista} step $\quad \mathbf{b}_l = \mathbf{W}_l \mathbf{y}$, lemma \ref{thm:matrix_vector} and \ref{thm:sum_vectors} describe the probabilistic variant of \textsc{lista} step $ \mathbf{c}_l = \mathbf{b}_l +\mathbf{S}$ and lemma \ref{thm:soft_thresholding} describes the soft-thresholding step $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$. Overall the probabilistic layer is described by theorem \ref{thm:prob_layer}.
